---
title: "Module B Practice Questions"
author: "Justin Roberts"
date: "2023-08-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## STAT 6021: Module B Practice Questions
### Topic B.2: Getting Started with R

#### 1.a) Read this data in and assign it to an object called cars.df

```{r}
cars.df<-mtcars
```

#### 1.b) Report how many observations and variables are in this dataset

cars.df has 32 observations of 11 variables

#### 2.a) Read "students.txt" in and assign it to an object called students.df

```{r}
students.df<-read.delim("/Users/Justin/Desktop/STAT 6021/students.txt")
```

#### 2.b) Report how many observations and variables are in this dataset

students.df has 249 observations of 9 variables

#### 3) Install Packages

In the IDE, I went to Tools, then Install Packages to select and install the listed packages

#### 4) Load faraway package, read in the dataset called cornnit and assign it to an object called corn.df

```{r}
corn.df<-faraway::cornnit
```

### Topic B.3: Data Types & Structures in R

#### 5) Are the following valid names for objects in R?

Yes - e, h
No - a, b, c, d, f, g

#### 6) Create a numeric vector with: 13, 91, 36, 95, 9, 3, 61, 20, 22, 97.  Assign them to a vector called practice and use R to find out if practice is a character, numeric, or logical type

```{r}
practice<-c(13,91,36,95,9,3,61,20,22,97)
is.numeric(practice)
is.character(practice)
is.logical(practice)
```

#### 7) For each of the following, determin if they are TRUE or FALSE.  Answer first then use R to confirm

TRUE - d, e
FALSE - a, b, c, f

```{r}
practice[5]==5
practice[10]!=97
(practice[1]+practice[2])<104
(practice[1]+practice[2])<=104
(practice[2]==91) & (practice[9]==22)
(practice[5]<9) | (practice[6]>=4)
```

#### 8) Create the matrix and assign it to the object Mat.A

```{r}
mat.A<-matrix(c(4,6,1,2,3,1), nrow = 2, ncol = 3)
mat.A
```

##### 8.a) Give the following column names to Mat.A: "Huey", "Dewey", "Louie"

```{r}
colnames(mat.A)<-c("Huey","Dewey","Louie")
mat.A
```

##### 8.b) What is the output if we type Mat.A[2,1]?

6

##### 8.c) What is the output if we type dim(Mat.A)?

2 3

#### 9) Convert the vector practice to a factor. What is the order of the levels in this factor?

Ascending order (smallest to largest)

```{r}
practice2<-factor(practice)
practice2
```

### Topic B.4: R Markdown
#### 10) Type up your answers to these questions using R Markdown and output an HTML file

See above
